TBD

### 2021-03-18 outputs/paper/paper.Rmd
Update Discussion, formula, citations

## Discuss the intervention
In this experiment, the intervention is receiving a concise informational message about the existence of deepfakes prior to the news feed treatment. The authors would like to analyze if receiving an information prompt about deepfakes before the news feed will affect the reliability and trustworthiness of all fake news clippings
Through this experiment, participants had the opportunity to detect fake media, enclosing a debrief which demonstrates how the deepfake process works. We believe that this experiment will help to educate the public about the growing ubiquity of deepfakes and the potential threat they might pose to information processing for the general public. By understanding how deepfakes function from their low-cost interventions, citizens can effectively prevent the harm caused by the misinformation.

@@

## FEATURE SELECTION

@@

## MULTIPLE LINEAR REGRESSION
We are using RStudio to run the multiple linear regression model. The following reasons explain why we decide to choose multiple linear regression:
* It account for all of the potentially important factors in one model
* It leads to a more precise understanding of the relationship between dependent variables and independent variables
* It is able to identify outliers or anomalies in the dataset.

@@

$$
\hat Y=\hat \beta_0+\sum_{a=male}^{other}\hat \beta_a*Gender_a+\sum_{b=High\ school}^{Postgraduate}\hat \beta_b*educ_b+\sum_{c=HHI25K\ -HHI49K}^{HHI>150K}\hat \beta_c*HHI_c+\sum_{d=Ethnicity:white}^{Ethnicity:black}\hat \beta_d*Ethnicity_d$$

$$+\sum_{e=Region:Northeast}^{Region:West}\hat \beta_e*Region_e+\hat \beta_{f}*I_{WaveID}+\hat \beta_{g}*I_{Meta:OSmobile}+\hat \beta_{h}*I_{Age>65}+\sum_{i=PID:Independent}^{Republican}\hat \beta_i*PID_i$$
$$+\hat \beta_{j}*{Ambivalent\ Sexism}+\hat \beta_{k}*{Polknow}+\sum_{l=treat:video}^{treat:ad}\hat \beta_l*Treat_l+\sum_{m=script:bidenshit}^{script:lgbtq}\hat \beta_m*Script_m+\hat \beta_{n}*I_{exp\_1\_prompt:\ info}$$

$$+\hat \beta_o*{post\_dig\_lit}+\hat \beta_p*{Internet\_usage}+\hat \beta_{q}*{CRT}+\epsilon$$

# Result

@@

### T test2

@@

### T test3

@@

### T test 4

@@

# Results

@@

## First discussion point

## Second discussion point

## Third discussion point

## Weaknesses and next steps

>>>>

## Intervention
In this experiment, the intervention is receiving a concise informational message about the existence of deepfakes prior to the news feed treatment. The authors would like to analyze if receiving an information prompt about deepfakes before the news feed will affect the reliability and trustworthiness of all fake news clippings
Through this experiment, participants had the opportunity to detect fake media, enclosing a debrief which demonstrates how the deepfake process works. We believe that this experiment will help to educate the public about the growing ubiquity of deepfakes and the potential threat they might pose to information processing for the general public. By understanding how deepfakes function from their low-cost interventions, citizens can effectively prevent the harm caused by the misinformation.

@@

## Feature Selection

@@

## Multiple Linear Regression
We are using RStudio to run the multiple linear regression model. The following reasons explain why we decide to choose multiple linear regression:
* It account for all of the potentially important factors in one model
* It leads to a more precise understanding of the relationship between dependent variables and independent variables
* It is able to identify outliers or anomalies in the dataset.

@@

$$\hat Y=\hat \beta_0+\sum_{a=male}^{other}\hat \beta_1\cdot Gender_a+\sum_{b=High\ school}^{Postgraduate}\hat \beta_2\cdot educ_b+\sum_{c=25K\ -49K}^{>150K}\hat \beta_3\cdot HHI_c+\sum_{d=white}^{black}\hat \beta_4\cdot Ethnicity_d$$

$$+\sum_{e=Northeast}^{West}\hat \beta_5\cdot Region_e+\hat \beta_{6}\cdot I_{WaveID}+\hat \beta_{7}\cdot I_{Meta:OSmobile}+\hat \beta_{8}\cdot I_{Age>65}+\sum_{i=Independent}^{Republican}\hat \beta_9\cdot PID_i
+\hat \beta_{10}\cdot {Ambivalent\ Sexism}+\hat \beta_{11}\cdot$$ $${Polknow}+\sum_{l=video}^{ad}\hat \beta_{12}\cdot Treat_l+\sum_{m=bidenshit}^{lgbtq}\hat \beta_{13}\cdot Script_m+\hat \beta_{14}\cdot I_{exp\_1\_prompt:\ info}$$

$$+\hat \beta_{15}\cdot {post\_dig\_lit}+\hat \beta_{16}\cdot {Internet\_usage}+\hat \beta_{17}\cdot {CRT}+\epsilon$$

@@

### t-test 2

@@

### t-test 3

@@

### t-test 4

@@

@@

Deepfake technology can be used against candidates to synthesize false videos, which would potentially disrupt the elections. The purpose of the research is to inform the public of the existence of deepfake technology and consequently to improve the resilience of democratic politics to this AI threat.

## Bias and ethical concerns

Some modelling bias and ethical concerns are addressed:

### Privacy problem on zip code
To protect the privacy of respondents in the experiment, detailed address information such as zip code was excluded from the linear regression model. Instead, location was proxied by region. Thereby, it would be impossible to reverse engineer the identity of the respondent by any ill-intended third parties. Furthermore, postal code is a proxy for socioeconomic status, which correlates with HHI (household income), causing multicollinearity and eventually biasing the coefficient [@citeCorrelation].

### Choice of candidate - election result disruption & pre-existing gender prejudice
The one-month experiment was run prior to the 2020 U.S. presidential election, to minimize the risk of influencing the election outcome and in the meantime to have discernible effect for the experiment, a high-profile candidate who was not finalisted to be the democratic nominee should be selected. In addition, we would like to test for the impact of pre-existing sexism against women among subjects on the effect of the deepfake. Elizabeth Warren came naturally to be our choice of the candidate who meets all the conditions above.

### Active debrief - post-experiment potential change in participants’ political behavior
At the completion of the survey, an extensive debrief was conducted on all subjects which instructed respondents to affirm that the treatment media about Elizabeth Warren was false. The active debrief was done to educate participants on deepfake media. And thus it would be unlikely for the treated group to change their political behavior later on as a post-exposure consequence.

## Model results

### Heterogeneity in different socioeconomic groups
As for the regression model result on affective response towards Elizabeth Warren, heterogeneous effects in respondents from different socioeconomic groups were observed. All else held constant, on average people with a postgraduate degree significantly favor Warren by 9.3 points more than people with lower than high school education. High-incomers with annual income above $100k favor Warren by 4 points more than people who earn less than $25,000 a year. In contrast, people who were unwilling to disclose their salaries disliked the candidate by 4.94 points compared to the low-incomers. Elderly people aged over 65 deduct feeling marks by 4.35 points towards Warren after being exposed to the deepfake media about Warren.

### Impact from partisan motivated reasoning and sexism discrimination
Partisanship accounts for a large part of the sentiment score towards Warren. For people supporting rival parties to the Democratic as the Republican and Independent, they substantially dislike Warren by about 40 and 27 points on average respectively compared with people identifying with the Democratic. Additionally, the map would also justify the positive coefficient for the Northeast region, where Warren is from; she is home based in Massachusetts [@citeWarrenBase]. For people holding ambivalent sexism views against women, a higher level in their hostile attitude would deduct 4 more marks from their feeling scales for the female candidate Warren on average.

### Deepfake and other false media, not that different in fooling the public
Although there is significant influence from the deepfake video on altering people’s sentiment towards the candidate, the two-sample t-test results between deepfake and other false media assure us that the its degree of detriment is no different from false audio or text in terms of deception and affective impression.

### Political knowledge and internet usage
It is worth our attention that compared to political knowledge, internet usage has a more significant effect on respondents’ affective impression. Perhaps that the more frequent interest users gain a more holistic understanding of political positions and current trends in the world thus they are more immune to the infamatory deepfake technologies.

## Real world implication
Based on the observed effects in affective response from different subject subgroups in the deepfake experiment, we conclude that deepfake can have real impact on the candidate through altering people’s perceptions and sentiment on the politicians. Once the participants believe the deepfake video content to be true, it is likely that they would negatively impact their impression on the politician. Elderly people, people holding hostile gender prejudice and those identifying with rival political parties are susceptible to the deepfake information; the impact can be observed through deducted affective score on the candidate. However, for people with a higher education degree, high-incomers, and people from the candidate’s home state, they tend to favor the politician more than other groups. Interestingly, political knowledge has less significant influence on participants’ affective response to the candidate than internet usage.

Nevertheless, the effect of deepfake videos on the election is no different than other false media such as audio and text in terms of affective manipulation done to tarnish the politician’s public image.

With the growing ubiquity of deepfake technology, here comes one more channel for the spread of misinformation. Given the deeply-rooted views in partisan motivated reasoning and gender discrimination, along with uneven distributed soicioeconomic resources for people to access proper knowledge and digital technology, the barriers to a democratic society largely come from people’s cognitive characteristics. Therefore, informing the public about the deepfake and digital technology is of top priority to curb the spread of misinformation in terms of deepfake technology.

## Potential caveats
Although Warren has long been delisted as a Democratic presidential candidate, she is still a salient politician. During the experiment time window from Sep. 29th to Oct. 29th 2020, Warren delivered a speech in Wisconsin on Oct. 16th to denounce Donald Trump [@citeWarrenCaveats]. Her public appearance might cause confusion to the experiment participants who happen to know about this news and potentially disturb the deepfake experiment result if the deepfake script content was somewhat related to the actual news.

## Internal validity & external validity of model

### Internal validity
The internal validity of the model can be justified by the procedures of sampling, randomization in experiment intervention, controlling for confounders and having sufficient sample size in the regression model, so that alternative explanations but the treatment can be eliminated from the cause of effect on the outcome.

**Sampling**: Subjects were stratified sampled at a nationally representative weight in this field experiment, and sample’s demographic traits were cross-compared with the demographic traits in the most recent Current Population Survey (CPS) to ensure the randomization in sampling which simulates real world demographic distributions.

**Randomization in intervention**: The intervention of whether receiving information about deepfakes before watching the newsfeed treatment was randomized to avoid this knowledge biasing their perceptions and behaviors and thus the experiment outcome.

**Controlling for confounders**: Potential confounders were controlled for in the regression model to avoid the omitted variable bias. For example, education, age, and household income (HHI) are assumed to correlate with deepfake deception and affective appeal through their correlation with digital literacy, internet usage, and political knowledge. Race, gender, and ethnicity correlate with partisanship. These variables were included into the model as predictors for measured affective responses.

**Sufficient sample size**: There were 5,750 subjects participated in the experiment and after cleaning of missing values, 4,131 rows of observations data were fed to the multiple linear regression model. The sample size was sufficient to bring about statistical power in conducting inference on variable significance.

### External validity
External validity of conclusion on deepfakes was enhanced by the use of 5 customized deepfake contents instead of recycling one well-recognized deepfake example in the treatment experiment. The sampling population is from the U.S. national level, so that the study conclusion and subject trait summary are applicable to the domestic level. The study consists of two waves between Sep. 29th and Oct. 29th. The repetition of experiment conducted at different time periods is to smooth out some possible time effects in the result. However, the model result cannot be generalized to outside the U.S. due to the limitation in the topic itself - U.S. presidential election.

## Weaknesses and opportunities for future work
### Weakness
**Discussion on race and ethnicity**: Despite the extensive investigation into the factors of perception bias in partisanship and gender prejudice on the impact of respondent’s sentiment score for the candidate under the deepfake scenario, the paper skips the discussion on race and ethnicity. Race and ethnicity are confounders that correlate with people’s party identification and affect people’s perception of the candidate as well [@citeRace].

**Democratic party only**: The paper chose the candidate to be a politician in the Democratic party, and focuses the topic on the Democratic election. It is possible that the experiment outcome was only valid for the analysis on Democratic party, especially supporter traits on socioeconomic and demographic characteristics.

**Within the U.S. only**: The nature of the U.S. domestic election topic limits the conclusion only applicable to regions within the U.S. on the study of political misinformation impact by deepfake media.

### Opportunities
The study investigates the impact of deepfake media on political misinformation through two field experiments conducted within a month period through the topic of 2020 Democratic presidential election. The external validity of the study can be further improved in order for the result to be generalizable to other political parties, time periods and situations. 
**Time window**: for the experiment time window, it can be prolonged or randomized in a series of experiment repetitions as long as they are conducted after the time point when the in-party presidential nominee has been finalized.

**Candidate from other parties**: The same experiment could be repeated using candidates from other parties (Republican, or Independent) to test the robustness and generalizability of the model result.

**Bayesian modelling**: The persuasion effect of deepfake on politics misinformation is measured through two channels, deception level and affective score. When interpreting the regression result on respondent’s affective response to the candidate in the deepfake experiment, the assumption is made that the viewer forms their belief on the media content before they change their mind on the involved candidate. We assume that the direction of change in affective score in the experiment is caused by whether the viewer believed the newsfeed content. A negative coefficient indicates that they were fooled by the content and thus further dislike Warren based on their belief in the false content. Bayesian inference modelling [@citeBayes] can be used to incorporate the conditional probability of whether the viewer believed the media content to be true into the analysis on affective response.

## Differences and difficulties
### Differences
**Feature selection**: Before building the multiple linear regression model, feature engineering was used to visualize feature importance and select the top 20 most important features from a total of 100 variables with the Random Forest classifier [@citeRandomforest]. The tree-based algorithm splits nodes based on how well they improve the purity of the node through maximizing information gain. The most informative features are at the start of the trees, and less relevant features are places at lower nodes. This process naturally ranks the importance of features, therefore it can be used for feature selection.

**Additional features**: Apart from the treatment variable and regressors describing demographic and socioeconomic traits (age, education, gender, party identification, political knowledge, metrics on internet usage, .etc) in the original model, the random forest algorithm identified household income (`HHI`), region, script type, and ethnicity as relevant features. Income confounds with deepfake deception and affective appeal through its correlation with digital literacy and internet usage. Region and ethnicity are correlated with partisanship. The five types of script contents were included to control for any differential effect of persuasion ability by deepfake.

**A different target variable, affective appeal**: The original model emphasized more on the study of deceptive level of deepfake technology. The persuasion power of deepfake can be measured through the channel of deception into believing and negative affect towards the politician. Furthermore, it is the consequence of the change in people’s affective response that influences the election outcome. Therefore, this paper decided to study the deepfake persuasive ability through the second channel, its impact on a candidate's affective appeal.

Based on the regression model result of adjusted R-squared, the model fit outperformed the regression on deceptive levels from the original paper (38% vs. 8%). Our model can explain more of the variations in a candidate's affective appeal to a great extent.

### Difficulties
**Missing values**: Every variable in the survey data was cleaned for missing or extreme values. Some columns have a large proportion of missing values and thus were removed. As for columns with a few missing records, these rows were omitted.

**Outliers and model fit**: When inspecting the residual vs. leverage plot obtained from the regression result, some extreme cases and influential points exist in the data, which might skew the overall linear model fit. To improve the model fit, a non-linear regression model such as random forest regression or Xgboost can be considered.
